The Impact of News Sentiment on MSFT

### 2023-12-09 MSFT.Rmd
fixed some bugs

```{r include=FALSE}
if (!require("vars")) install.packages("vars", dependencies=TRUE)
if (!require("tseries")) install.packages("tseries", dependencies=TRUE)
if (!require("quantmod")) install.packages("quantmod", dependencies=TRUE)
if (!require("PerformanceAnalytics")) install.packages("PerformanceAnalytics", dependencies=TRUE)
if (!require("forecast")) install.packages("forecast", dependencies=TRUE)
if (!require("rugarch")) install.packages("rugarch", dependencies=TRUE)
if (!require("tinytex")) install.packages("tinytex", dependencies=TRUE)
if (!require("zoo")) install.packages("zoo", dependencies=TRUE)
if (!require("ggpl")) install.packages("ggpl", dependencies=TRUE)

library(PerformanceAnalytics)
library(forecast)
library(rugarch)
library(vars)
library(tseries)
library(quantmod)
library(tinytex)
library(zoo)
library(ggpl)
```
# Insert introduction here
In recent years Microsoft has pushed and achieved great progress in a diverse portfolio of technologies (Microsoft, 2022) including also partnerships with AI research centers such as OpenAI. Alongside this development, its stock price has since reached new all-time highs and persists to be a major player in tech investments.

@@

MSFT_ARMA <- auto.arima(MSFT_returns_train)
MSFT_ARMA_pred <- forecast(MSFT_benchmark_ARMA, level=95, h = length(news_test))
plot(MSFT_ARMA_pred)

>>>>

```{r include=FALSE}
if (!require("vars")) install.packages("vars", dependencies=TRUE)
if (!require("tseries")) install.packages("tseries", dependencies=TRUE)
if (!require("quantmod")) install.packages("quantmod", dependencies=TRUE)
if (!require("PerformanceAnalytics")) install.packages("PerformanceAnalytics", dependencies=TRUE)
if (!require("forecast")) install.packages("forecast", dependencies=TRUE)
if (!require("rugarch")) install.packages("rugarch", dependencies=TRUE)
if (!require("tinytex")) install.packages("tinytex", dependencies=TRUE)
if (!require("zoo")) install.packages("zoo", dependencies=TRUE)
if (!require("ggplot2")) install.packages("ggplot2", dependencies=TRUE)

library(PerformanceAnalytics)
library(forecast)
library(rugarch)
library(vars)
library(tseries)
library(quantmod)
library(tinytex)
library(zoo)
library(ggplot2)
```
# Insert introduction here
In recent years Microsoft has pushed and achieved great progress in a diverse portfolio of technologies (Microsoft, 2022) including also partnerships with AI research centers such as OpenAI. Alongside this development, its stock price has since reached new all-time highs and persists to be a major player in tech investments.

@@

MSFT_ARMA <- auto.arima(MSFT_returns_train)
MSFT_ARMA_pred <- forecast(MSFT_ARMA, level=95, h = length(news_test))
plot(MSFT_ARMA_pred)
